### 2015-04-13 src/paper2/paper2.tex
Updated panel labels

@@

	\caption{(A) Top-view illustrating three key events within the experiment. Left panel: At the extreme right position, the reference target (R) is flashed. Middle panel: The participant moves while keeping fixation on the fixation point (FP). Right panel: At the left most position, one of the probe locations (P) is flashed. (B) Timing of key events. Within a run of sinusoidal sled motion, participants always fixated the fixation point. At the rightmost point, the reference (R) was flashed for 50 \si{\milli\second}. Then, at the extreme left position, a probe (P) was shown for 50 \si{\milli\second}. Participants responded whether the probe was presented to the left or right of the reference using a joystick. (C) Locations of fixation points (plus signs) and reference/probe locations (bars) used in our experiment (see also \tabref{p2:tab1}).}

@@

    \caption{Performance in one subject (S1). The proportion of rightward responses is plotted against probe location relative to the reference. Size of a data point represents the number of trials tested. Solid lines, best-fit cumulative Gaussians, characterized by bias (l) and standard deviation (r). (A) Constant reference depth, variable fixation depth, 150 \si{\milli\metre} translation. (B) Constant reference depth, variable fixation depth, 300 \si{\milli\metre} translation. (C) Variable reference depth, constant fixation depth, 150 \si{\milli\metre} translation. (D) Variable reference depth, constant fixation depth, 300 \si{\milli\metre}  translation.}

@@

    \caption{Top view of the updating biases ($\mu$). Dots, individual bias values; error bars, averages (\textpm SD) across participants; +, fixation point. (A), (B), (C), (D): Conditions as in Figure \ref{p2:fig2}.}

@@

    \caption{Head- versus gaze-centered effects in updating bias (l). (A) Average bias (6 SE) across participants plotted against head- centric version angle of fixation point, for each of the 16 conditions. (B) Same data plotted as a function of head-centric angle to the reference location. (C) Same data plotted against the gaze-centric location of the reference target. Open symbols, 150 mm translation. Closed symbols, 300 mm translation. Circles, constant fixation depth. Squares, constant reference depth. Color scheme as in Figure \ref{p2:fig1}C.}

>>>>

\label{p2}

@@

	\caption{\panel{A} Top-view illustrating three key events within the experiment. Left panel: At the extreme right position, the reference target (R) is flashed. Middle panel: The participant moves while keeping fixation on the fixation point (FP). Right panel: At the left most position, one of the probe locations (P) is flashed. \panel{B} Timing of key events. Within a run of sinusoidal sled motion, participants always fixated the fixation point. At the rightmost point, the reference (R) was flashed for 50 \si{\milli\second}. Then, at the extreme left position, a probe (P) was shown for 50 \si{\milli\second}. Participants responded whether the probe was presented to the left or right of the reference using a joystick. \panel{C} Locations of fixation points (plus signs) and reference/probe locations (bars) used in our experiment (see also \tabref{p2:tab1}).}

@@

    \caption{Performance in one subject (S1). The proportion of rightward responses is plotted against probe location relative to the reference. Size of a data point represents the number of trials tested. Solid lines, best-fit cumulative Gaussians, characterized by bias (l) and standard deviation (r). \panel{A} Constant reference depth, variable fixation depth, 150 \si{\milli\metre} translation. \panel{B} Constant reference depth, variable fixation depth, 300 \si{\milli\metre} translation. \panel{C} Variable reference depth, constant fixation depth, 150 \si{\milli\metre} translation. \panel{D} Variable reference depth, constant fixation depth, 300 \si{\milli\metre}  translation.}

@@

    \caption{Top view of the updating biases ($\mu$). Dots, individual bias values; error bars, averages (\textpm SD) across participants; +, fixation point. \panel{A} to \panel{D}: Conditions as in Figure \ref{p2:fig2}.}

@@

    \caption{Head- versus gaze-centered effects in updating bias (l). \panel{A} Average bias (6 SE) across participants plotted against head- centric version angle of fixation point, for each of the 16 conditions. \panel{B} Same data plotted as a function of head-centric angle to the reference location. \panel{C} Same data plotted against the gaze-centric location of the reference target. Open symbols, 150 mm translation. Closed symbols, 300 mm translation. Circles, constant fixation depth. Squares, constant reference depth. Color scheme as in Figure \ref{p2:fig1}C.}
